Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-12-01 Paper/main.tex
Nate initial intro changes

In addition to these measurements, large eddy simulations (LES) have
also been used to study ABL stability characteristics.  Recent work by
Kaul et al. \cite{kaul2020large} has shown that LES computations using
Nalu-Wind can capture the neutrally and convectively unstable onshore
ABL.  Previous simulations by Cheung et al. \cite{cheung2020large}
successfully replicated the unstable and neutral ABL corresponding to
the Cape Wind meteorological tower measurements
\cite{archer2016predominance} and showed the effects of surface
heating on atmospheric stratification.  Additional LES computations
\cite{sullivan2016turbulent} have also previously explored stable
conditions of onshore boundary layers, such as the GABLS1 boundary
layer \cite{beare2006intercomparison}.  However, a complete comparison
including offshore stable ABL conditions has yet to be completed.

\subsection{Prevous work}

\fxnote{Nate's piece goes here.  Edit and merge with above.}

Stably stratified boundary layers, or SBL, commonly occur on clear nights over land, in polar regions, and over cold oceans. Given that wind turbines are likely to experience the SBL as part of the diurnal cycle, or as part of there general locale, it is of utmost import to model such conditions correctly. Large eddy simulation, or LES, of the SBL presents certain challenges compared to neutral and convective stability states, stemming primarily from small dominant eddy length scales and low turbulence intensity. These challenges require higher resolution grids and/or advanced subgrid scale (SGS) models. As such, LES research of the SBL has been slower to evolve than the other stability states.

The first successful LES of the SBL was published by Mason and Derbyshire in 1990 \cite{Mason1990}. They used a strategy of simulating a near steady-state neutral stability turbulent simulation, then added a cooling-surface boundary to develop the stable ABL. They recorded a need for implausibly strong initial perturbations to sustain turbulence using the Smagorinsky SGS model. Brown et al.\ \cite{Brown1994} worked with Mason and Derbyshire to add stochastic backscatter to the SGS model, resulting in better agreement with surface layer observations. Andren, \cite{Andren1995}, simulated two SBL types, one with a neutral layer aloft, and one capped by an inversion, comparing two SGS models. He found significant improvements with the Sullivan SGS model, on par with the earlier backscatter model. In 1995, Derbyshire flew two measurement balloons, one in a heterogeneous location, another in a more idealized location, with the hope that the measurements would be useful for comparison to LES. He found significant variation in the critical Richardson number, and the temperature structure led him to state that complete comparison with LES had little point. Kemp and Thompson \cite{Kemp1996} used the same model as \cite{Brown1994} to study particle dispersion, but the LES code did not replicate an expected plume growth. Derbyshire wrote a review of SBL modeling along with future projections in 1999 \cite{Derbyshire1999}, with discussion of the importance of local Richardson number, a general statement that LES is a good supplement to SBL observations, and identification of a need to go to higher resolutions in SBL research.

@@

An inter-comparison of LES simulations of the SBL was organized in 2006, the results of which are published in Beare et al.\ \cite{Beare2006}. Collectively, this is knows as the GABLS initiative, and involved simulating a moderately stable flow taken from Kosovic and Curry \cite{Kosovic2000}. Eleven codes were compared in all, and in general, grid deltas of less than 12.5m were found successful at maintaining resolved turbulence, and at grid deltas less than 3.125m showed little statistical change. The comparison also identified that Smagorinsky constants less than 0.2 were desirable, and that results became independent of SGS at 1m resolution. In the same year, Kumar et al. \cite{Kumar2006} successfully simulated an entire diurnal cycle with LES using a Lagrangian dynamic scale dependent SGS model. Stoll and Porte-Agel \cite{Stoll2007} compared three grid refinements and three scale dependent dynamic SGS models, showing that the Lagrangian and locally averaged models reproduced important flow features. The work of van Dop and Axelsen \cite{vanDop2007} provided even more evidence in support Nieuwstadt's local scaling hypothesis for SBLs. Chow and Zhou \cite{Chow2011} showed evidence that the Smagorinsky model is simply too dissipative for use in strongly stable flows.

The scale dependent Lagrangian SGS model has been used by several researchers since 2011, including Lu and Porte-Agel \cite{Lu2011}, Huang and Bou-Zeid \cite{Huang2013}, Park et al.\ \cite{Park2014}, and Abkar and Porte-Agel \cite{Abkar2015}. Recent work in LES of the SBL includes Matheou \cite{Matheou2016} who explored a large parameter space using the Smagorinsky-Lilly SGS closure. Several researchers have applied SBL simulation in the wind energy space \cite{Aitken2014, Abkar2015, Ghaisas2017}. This year, Wurps et al. \cite{Wurps2020} provided a rigorous grid resolution study for the SBL, looking at mean flow, turbulence variables, and two-point correlations, using a dynamic SGS model that allows backscatter. They found grid requirements to be 2.5m, 10m, and 20m for stable, neutral, and convective boundary layers respectively. They also found Pope's resolution requirement ratio of resolved energy to total energy of $\gamma < 0.8$ to be too lax in many cases. They advocate looking at two point correlations in order to quantify flow structure size, which in turn provides a basis for choice of grid resolution.

>>>>

\subsection{Previous Simulation Work}

In addition to these measurement campaigns, large eddy simulations (LES) have
also been used to study ABL stability characteristics.  Recent work by
Kaul et al. \cite{kaul2020large} has shown that LES computations using
Nalu-Wind can capture the neutrally and convectively unstable onshore
ABL.  Previous simulations by Cheung et al. \cite{cheung2020large}
successfully replicated the unstable and neutral ABL corresponding to
the Cape Wind meteorological tower measurements
\cite{archer2016predominance} and showed the effects of surface
heating on atmospheric stratification. LES of the stable ABL (SBL) presents 
certain challenges compared to neutral and convective stability states, stemming 
primarily from small dominant eddy length scales and low turbulence intensity. 
These challenges require higher resolution grids and/or advanced subgrid 
scale (SGS) models. As such, LES research of the SBL has been slower 
to evolve than the other stability states.

The first successful LES of the SBL was published by Mason and Derbyshire in 
1990 \cite{Mason1990}. They used a strategy of simulating a near steady-state 
neutral stability turbulent simulation, then added a cooling-surface boundary 
to develop the stable ABL. They recorded a need for implausibly strong initial 
perturbations to sustain turbulence using the Smagorinsky SGS model. Brown et 
al.\ \cite{Brown1994} worked with Mason and Derbyshire to add stochastic backscatter 
to the SGS model, resulting in better agreement with surface layer observations. 
Andren, \cite{Andren1995}, simulated two SBL types, one with a neutral layer aloft, and 
one capped by an inversion, comparing two SGS models. He found significant improvements 
with the Sullivan SGS model, on par with the earlier backscatter model. Kemp and 
Thompson \cite{Kemp1996} used the same model as \cite{Brown1994} to study particle 
dispersion, but the LES code did not replicate an expected plume growth. Derbyshire 
wrote a review of SBL modeling along with future projections in 1999 \cite{Derbyshire1999}, 
noting the importance of local Richardson number and identifying a need to go 
to higher resolutions in SBL research.

@@

An inter-comparison of LES simulations of the SBL was organized in 2006, the 
results of which are published in Beare et al.\ \cite{Beare2006}. Collectively, 
this is knows as the GABLS initiative, and involved simulating a moderately 
stable flow taken from Kosovic and Curry \cite{Kosovic2000}. Eleven codes 
were compared in all, wherein grid deltas of less than 12.5m were found to 
successfully maintain resolved turbulence, grid deltas less than 3.125m 
showed little statistical change, and results became independent of SGS 
modeling at 1m resolution. In the same year, Kumar et al. \cite{Kumar2006} 
successfully simulated an entire diurnal cycle with LES using a Lagrangian 
dynamic scale dependent SGS model. This model has been used by several 
researchers since 2011, including Lu and Porte-Agel \cite{Lu2011}, Huang 
and Bou-Zeid \cite{Huang2013}, Park et al.\ \cite{Park2014}, and 
Abkar and Porte-Agel \cite{Abkar2015}. Stoll and Porte-Agel \cite{Stoll2007} 
compared three grid refinements and three scale dependent dynamic SGS models, 
showing that the Lagrangian and locally averaged models reproduced important 
flow features. The work of van Dop and Axelsen \cite{vanDop2007} provided 
even more evidence in support Nieuwstadt's local scaling hypothesis for SBLs. 
Chow and Zhou \cite{Chow2011} showed evidence that the Smagorinsky model is 
simply too dissipative for use in strongly stable flows.

More recent work in LES of the SBL includes Matheou \cite{Matheou2016} who 
explored a large parameter space using the Smagorinsky-Lilly SGS 
closure, as well as Sullivan et al.\ \cite{sullivan2016turbulent}. Several researchers 
have applied SBL simulation in the wind energy space \cite{Aitken2014, Abkar2015, Ghaisas2017}. 
This year, Wurps et al. \cite{Wurps2020} provided a rigorous grid resolution study for the SBL, 
looking at mean flow, turbulence variables, and two-point correlations, using a dynamic 
SGS model that allows backscatter. They found grid requirements to be 2.5m, 10m, and 20m 
for stable, neutral, and convective boundary layers respectively. They advocate looking 
at two point correlations in order to quantify flow structure size, which in turn 
provides a basis for evaluating grid resolution. In all of the reviewed literature, SBL LES 
has been run in the onshore context only, a complete comparison
including offshore stable ABL conditions has yet to be completed.
